The Evolution of Phenotypically Invariant Genetic Networks

### 2017-06-20 handnotes.tex
minor editing

  Organisms' phenotypes are constructred by gene by gene by environment interactions. Here we simply define the phenotype to be the organismal temporal molecular dynamics directly under natural selection. The \emph{what}, \emph{when}, and \emph{where}, of an organism's molecules that are physiologically or otherwise relevant for survival. 
  \jss{  Thus we say that some function $\phi(t)$ is a phenotype where, 
  \begin{align}
    \phi(t) = \int_{0}^{\infty} h(t) u(t) dt  ,
  \end{align}
  and $h(t)$ is the \emph{impulse response} of the system and $u(t)$ is the \emph{input} function, both functions of time $t$. The input can be interpreted as the environment, as initial conditions, or otherwise, depending on the biological specifics under study. The phenotype is a convolution of both the impulse response and the input, as allowed by our assumption of linearity.

>>>>

  \jss{Organisms' phenotypes are constructred by gene by gene by environment interactions. Here we simply define the phenotype to be the organismal temporal molecular dynamics directly under natural selection. The \emph{what}, \emph{when}, and \emph{where}, of an organism's molecules that are physiologically or otherwise relevant for survival. 
   Thus we say that some function $\phi(t)$ is a phenotype where, 
  \begin{align}
    \phi(t) = \int_{0}^{\infty} h(t) u(t) dt  ,
  \end{align}
  and $h(t)$ is the \emph{impulse response} of the system and $u(t)$ is the \emph{input} function, both functions of time $t$. The input can be interpreted as the environment, as initial conditions, or otherwise, depending on the biological specifics under study. The phenotype is a convolution of both the impulse response and the input, as allowed by our assumption of linearity.
